Section rings of $\bq$-divisors on minimal rational surfaces

### 2017-12-19 surfaces-write-up/Landesman-Ruhm-Zhang-Rational-Surfaces-MRL.tex
MRL style update

%%%%%%%%%%%%%%%%%%%%%
%   AMS packages    %
%%%%%%%%%%%%%%%%%%%%%
\documentclass{amsart}

@@

@@

\author{Aaron Landesman}
\address[Aaron Landesman]{Department of Mathematics, Stanford University}
\email{aaronlandesman@stanford.edu}

\author{Peter Ruhm}
\address[Peter Ruhm]{Department of Mathematics, Stanford University}
\email{pruhm@stanford.edu}

\author{Robin Zhang}
\address[Robin Zhang]{Department of Mathematics, Columbia University}
\email{rzhang@math.columbia.edu}

@@

\section{Acknowledgments}
\label{sec:ack}
We are grateful to David Zureick-Brown for offering great advice on
this project, for many useful suggestions on this paper, and for
many valuable conversations. We thank Peter
Landesman and Shou-Wu Zhang for offering helpful comments and
suggestions for this paper. We also thank Ken Ono and the
Emory University Number Theory REU for arranging our project and
for the great support that we have received. Finally, we would like to acknowledge the
support of the National Science Foundation (grant number DMS-1250467).

@@

\nocite{*}
\bibliography{bibliography-stacky-surface}
\bibliographystyle{alpha}

>>>>

%%%%%%%%%%%%%%%%%%%%%
%   AMS packages    %
%%%%%%%%%%%%%%%%%%%%%
\documentclass{mrlart7}

@@

%% MRL requirements
	\def\volno{18}
	\def\yrno{2011}
	\def\issueno{00}
	\setcounter{page}{10001}
	\def\lpageno{100NN} %temporary numbers
  %%replace NN with the pagelength of the paper%%
	\overfullrule=5pt

@@

\author{Aaron Landesman}
\address[Aaron Landesman]{Department of Mathematics \\ Stanford University}
\urladdr{http://web.stanford.edu/$\sim$aaronlan/}
\email{aaronlandesman@stanford.edu}

\author{Peter Ruhm}
\address[Peter Ruhm]{Department of Mathematics \\ Stanford University}
\email{pruhm@stanford.edu}

\author{Robin Zhang}
\address[Robin Zhang]{Department of Mathematics \\ Columbia University}
\urladdr{http://math.columbia.edu/$\sim$rzhang/}
\email{rzhang@math.columbia.edu}

@@

\section*{Acknowledgments}
\label{sec:ack}
We are grateful to David Zureick-Brown for offering great advice on
this project, for many useful suggestions on this paper, and for
many valuable conversations. We thank Peter
Landesman and Shou-Wu Zhang for offering helpful comments and
suggestions for this paper. We also thank Ken Ono and the
Emory University Number Theory REU for arranging our project and
for the great support that we have received. Finally, we would like to acknowledge the
support of the National Science Foundation (grant number DMS-1250467).

@@

\nocite{*}
\bibliography{bibliography-stacky-surface}
\bibliographystyle{mrl}
